Gozde and Liora's Replication Code

### 2015-05-11 replication project.Rmd
edits and improvements

---
title: "Gozde and Liora Replication Code"
author: "Gozde Guran and Liora Goldensher"
date: "3/6/2015"
output: html_document
---

@@

library(MASS)
library(nlme)
library(xtable)
library(foreign)
library(dplyr)
library(broom)
library(ggplot2)
library(xtable)
library(stargazer)
library(grid)
library(gridExtra)

@@

# Cleaning up data
data <- rename(data, ext_vote = rexvote)
data <- rename(data, age_1 = age1) # (18–29 years)
data <- rename(data, age_2 = age2) # (30–45 years)
data <- rename(data, age_4 = age4) # (>65 years)
data <- rename(data, edu_1 = mye1) # Education: middle/high
data <- rename(data, edu_2 = mye2) # Education: university
data <- rename(data, farmer_own = farmerown) 
data <- rename(data, left_right_scale = zlrs) # Left-Right Scale
data <- rename(data, eu_neg = euschlecht) # Negative evaluation of EU membership of one's own country
data <- rename(data, z_dem_satis = zsatisdmo) # Dissatisfied: Democracy
data <- rename(data, dispro_elect = disp) # Disproportionality
data <- rename(data, federalism = lfed1) # Decentralization
data <- rename(data, z_asylumseeker = zasylumseekers) 
data <- rename(data, z_unemp = zsur) # Unemployment rate
data <- rename(data, z_replacement = zreplacementrate) # Unemp benefits
data <- rename(data, max_er = rmax) # Maximum toughness in extreme right discourse

```

# Preparing data for analysis

@@

# Table 1
![Table 1](figures/table1.png)
```{r}
# Create vectors of coefficients, standard deviations, and variable names

coefficient <- as.vector(model$coef$fixed) 
n <- c(174452, 267)
stand_dev <- as.vector(sqrt(diag(model$varFix)))

# Create matrix of coefficients and standard deviations.

table_matrix <- cbind(coefficient, stand_dev)

@@

table_1 <- stargazer(table_matrix, title = "TABLE 1 Support for the Extreme Right: Sociodemographics, Attitudes, Country Effects, and Contextual Variables", align = TRUE, table.layout = "t", notes = "Logistic multilevel model. PQL2 estimates and model-based standard errors.", style = "ajps", out = "Table 1.html", no.space = TRUE)

```

# Figure 1 (Conditonal Effects of Unemployment and Immigration)
![Figure 1](figures/fig1.png)
```{r}
library(msm)
asy <- seq(from = min(data$z_asylumseeker), to = max(data$z_asylumseeker), by = .01) # vector with possible values for asylumseekers

variable <- asy # identifying "asy" as the variable of interest so that the remaining code can be reused in the next graph with a different variable of interest specified
slopes <- model$coef$fixed["z_unemp"] + model$coef$fixed["z_asylumseeker:z_unemp"] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for each variable 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop using the deltamethod function which approximates standard errors of transformation of parameters based on the given estimates of the mean and covariance (~ bootstrapping).
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x17) + (x36) * j, estmean, estvar)
}

# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

# Creating the first graph with ggplot

variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Asylumseekers"
ytitle <- "Effect: Unemployment"
main <- "Figure 1: The Conditional Effects of Unemployment and Immigration"
graph_1 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
  geom_line(aes(y = slopes), color = "blue") + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  geom_hline(yintercept = 0, size = 0.4, color = "black") +
  labs(x = xtitle, y = ytitle, title = main) +
  coord_fixed(ratio = 8)

#Figure 1, graph 2

unemployment <- seq(from = min(data$z_unemp), to = max(data$z_unemp), by = .01) # vector with possible values for unemployment
variable <- unemployment # standardized label
slopes <- model$coef$fixed["z_asylumseeker"] + model$coef$fixed["z_asylumseeker:z_unemp"] * variable # Estimated slopes based on estimated coefficients of asylumseekers (16) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x16) + (x36) * j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

# Creating the second graph with ggplot:

variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Unemployment"
ytitle <- "Effect: Asylum seekers"
main <- "The Conditional Effects of Unemployment and Immigration"
graph_2 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
  geom_line(aes(y = slopes), color = "blue") + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  geom_hline(yintercept = 0, size = 0.4, color = "black") +
  labs(x = xtitle, y = ytitle) +
  coord_fixed(ratio = 12)

# Figure 1 with ggplot

grid.arrange(graph_1, graph_2, ncol = 1)

# Plot separately - better scaled
graph_1
graph_2

```

@@

```{r}
# Figure 2, graph 1
# Create vector with possible values for salience
salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by = .1) 
variable <- salience
slopes <- model$coef$fixed["var_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x21) + (x39)*j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96*se
lower <- slopes - 1.96*se
variable.data <- cbind(variable, slopes, upper, lower)

# Creating the first graph with ggplot:

variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Salience"
ytitle <- "Effect: Variance"
main <- "The Conditional Effects of Salience and Variance"
graph_3 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
  geom_line(aes(y = slopes), color = "blue") + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  geom_hline(yintercept = 0, size = 0.4, color = "black") +
  labs(x = xtitle, y = ytitle, title = main) +
  coord_fixed(ratio = 400)

# Second part of Figure 2:

variance <- seq(from = min(data$var_c), to = max(data$var_c), by=10) # vector with possible values for variance
variable <- variance
slopes <- model$coef$fixed["salience_mean_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (20) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors

for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x20) + (x39) * j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

# Creating the second graph with ggplot:

variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Variance"
ytitle <- "Effect: Salience"
main <- "The Conditional Effects of Salience and Variance"
graph_4 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
  geom_line(aes(y = slopes), color = "blue") + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  geom_hline(yintercept = 0, size = 0.4, color = "black") +
  labs(x = xtitle, y = ytitle, title = main) +
  coord_fixed(ratio = 500)

>>>>

---
title: "Gozde and Liora's Replication Code"
author: "Gozde Guran and Liora Goldensher"
date: "3/6/2015"
output: html_document
---

@@

library(MASS) # includes the glmmPQL function to run model
library(nlme) # for non-linear mixed effects models
library(foreign) # allows us to read in data from another format
library(dplyr) # allows us to manipulate our dataset
library(broom) # helps tidy data and present in a more usable form
library(ggplot2) # for graphing
library(stargazer) # used to create regression tables
library(grid) # used to combine ggplot graphs
library(gridExtra) # used to combine ggplot graphs
library(msm) #includes deltamethod function, which allows us to obtain standard errors of transformed parameters

@@

# Cleaning up data
data <- data %>%
  rename(ext_vote = rexvote,
         age_1 = age1, # (18–29 years)
         age_2 = age2, # (30–45 years)
         age_4 = age4, # (>65 years)
         edu_1 = mye1, # Education: middle/high
         edu_2 = mye2, # Education: university
         farmer_own = farmerown,
         left_right_scale = zlrs, # Left-Right Scale
         eu_neg = euschlecht, # Negative evaluation of EU membership of one's own country
         z_dem_satis = zsatisdmo, # Dissatisfied: Democracy
         dispro_elect = disp, # Disproportionality
         federalism = lfed1, # Decentralization
         z_asylumseeker = zasylumseekers,
         z_unemp = zsur, # Unemployment rate
         z_replacement = zreplacementrate, # Unemp benefits
         max_er = rmax) # Maximum toughness in extreme right discourse
```

# Preparing data for analysis
Lines 64-83 of this code are based on (though not identical to) the code written by Harvard students in their previous replication of this paper. Citation : Noam Gidron; Jeffrey Javed, 2011, "Replication data for: The Unholy Trinity: Immigration, Unemployment and Extremism in Europe, 1980-2002", http://hdl.handle.net/1902.1/15902 V1

@@

# Table 1
![Table 1](figures/table1.png)
```{r}
# Create vectors of coefficients, standard errors, and variable names

coefficient <- as.vector(model$coef$fixed) 
standard_error <- as.vector(sqrt(diag(model$varFix)))

# Create matrix of coefficients and standard deviations.
table_matrix <- cbind(coefficient, standard_error)

@@

stargazer(table_matrix, title = "TABLE 1 Support for the Extreme Right: Sociodemographics, Attitudes, Country Effects, and Contextual Variables", align = TRUE, table.layout = "t", type = "text", notes = "Logistic multilevel model. PQL2 estimates and model-based standard errors.", style = "ajps", out = "Table 1.html", no.space = TRUE)
```

# Figure 1 (Conditonal Effects of Unemployment and Immigration)
![Figure 1](figures/fig1.png)
```{r}
#Function with which we will create each graph
graph <- function(data, ratio, ymin, ymax) {
  ggplot(data, aes(x = variable, y = slopes)) + 
  geom_line(aes(y = slopes), color = "blue") + #color will always be blue
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  geom_hline(yintercept = 0, size = 0.4, color = "black") + #fixed y intercept and color
  labs(x = xtitle, y = ytitle, title = main) + #titles will call from prepared data
  coord_fixed(ratio)
}
#Preparing the data for the first graph
asy <- seq(from = min(data$z_asylumseeker), to = max(data$z_asylumseeker), by = .01) # vector with possible values for asylumseekers
variable <- asy # identifying "asy" as the variable of interest so that the remaining code can be reused in the next graph with a different variable of interest specified
slopes <- model$coef$fixed["z_unemp"] + 
  model$coef$fixed["z_asylumseeker:z_unemp"] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for each variable 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop using the deltamethod function which approximates standard errors of transformation of parameters based on the given estimates of the mean and covariance (~ bootstrapping).
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x17) + (x36) * j, estmean, estvar)
}

# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)
variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Asylumseekers"
ytitle <- "Effect: Unemployment"
main <- "Figure 1: The Conditional Effects of Unemployment and Immigration"

#creating the first graph using our ggplot function
graph_1 <- graph(data = variable.data, ratio = 8)
graph_1

#Preparing the data for the second graph
unemployment <- seq(from = min(data$z_unemp), to = max(data$z_unemp), by = .01) # vector with possible values for unemployment
variable <- unemployment # standardized label
slopes <- model$coef$fixed["z_asylumseeker"] + model$coef$fixed["z_asylumseeker:z_unemp"] * variable # Estimated slopes based on estimated coefficients of asylumseekers (16) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x16) + (x36) * j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)
variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Unemployment"
ytitle <- "Effect: Asylum seekers"
main <- "The Conditional Effects of Unemployment and Immigration"
#Creating the second graph with our function
graph_2 <- graph(data = variable.data, ratio = 12)
graph_2

# Figure 1 with ggplot
grid.arrange(graph_1, graph_2, ncol = 1)

# Plot separately - better scaled
graph_1
graph_2
```

@@

```{r}
# Figure 2, graph 1
#Preparning the data to graph
salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by=.1) # vector with possible values for salience
variable <- salience
slopes <- model$coef$fixed["var_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x21) + (x39)*j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96*se
lower <- slopes - 1.96*se
variable.data <- cbind(variable, slopes, upper, lower)
variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Salience"
ytitle <- "Effect: Variance"
main <- "The Conditional Effects of Salience and Variance"

#Creating the first graph with our function
graph_3 <- graph(data = variable.data, ratio = 400)
graph_3

# Second part of Figure 2:
#Preparing the data to graph
variance <- seq(from = min(data$var_c), to = max(data$var_c), by=10) # vector with possible values for variance
variable <- variance
slopes <- model$coef$fixed["salience_mean_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (20) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors

for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x20) + (x39) * j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)
variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Variance"
ytitle <- "Effect: Salience"
main <- "The Conditional Effects of Salience and Variance"

#Creating the second graph with our function
graph_4 <- graph(data = variable.data, ratio = 500)
graph_4
